\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2014-09-23 paper/subdocuments/results.Rnw

# Export data to use with Stata
habe_bd_2010 <- rbind(data.frame(cbind("income" = habe10$psteink,"group"=0,"weight"=habe10$gew)),data.frame("income" = bd.2010.ind,"group"=1,"weight"=1))
habe_bd_2010$group <- factor(habe_bd_2010$group,labels=c("habe","bd"))
write.dta(habe_bd_2010, file="../../data/stata_data/habe_bd_2010.dta")

@@

# Select unmarried - HABE
habe10<-habe0911 %.% 
  filter(Jahr08==2010)
habe10.unmarried<-habe0911 %.% 
  filter(Familientyp08<140,Jahr08==2010)
habe10.unmarried<-data.frame(habe10.unmarried$VerfuegbaresEinkommen08)
names(habe10.unmarried)<-"inc_habe"
habe10.unmarried$inc_habe[habe10.unmarried$inc_habe<0]<-0 # One values is -20'000
habe10.unmarried$inc_habe<-habe10.unmarried$inc_habe*12/1000 # transform from monthly income to income per year

@@

# Export data to use with Stata
habe_bd_2010_unmarried <- rbind(data.frame(cbind("income" = habe10.unmarried$inc_habe,"group"=0)),data.frame("income" = bd.2010.ind,"group"=1))
habe_bd_2010_unmarried$group <- factor(habe_bd_2010_unmarried$group,labels=c("habe","bd"))
write.dta(habe_bd_2010_unmarried, file="../../data/stata_data/habe_bd_2010_unmarried.dta")

>>>>

# Export data to use with Stata (psteink durch VerfuegbaresEinkommen08 ersetzt)
habe_bd_2010 <- rbind(data.frame(cbind("income" = habe10$VerfuegbaresEinkommen08,"group"=0,"weight"=habe10$gew)),data.frame("income" = bd.2010.ind,"group"=1,"weight"=1))
habe_bd_2010$group <- factor(habe_bd_2010$group,labels=c("habe","bd"))
write.dta(habe_bd_2010, file="../../data/stata_data/habe_bd_2010.dta")

@@

# Select unmarried - HABE
habe10<-habe0911 %.% 
  filter(Jahr08==2010)
habe10.unmarried<-habe0911 %.% 
  filter(Familientyp08<140,Jahr08==2010) %.%
  select(VerfuegbaresEinkommen08,jahresgewicht)
#habe10.unmarried<-data.frame(habe10.unmarried$VerfuegbaresEinkommen08)

names(habe10.unmarried)<-c("inc_habe","gew")
habe10.unmarried$inc_habe[habe10.unmarried$inc_habe<0]<-0 # One values is -20'000
habe10.unmarried$inc_habe<-habe10.unmarried$inc_habe*12/1000 # transform from monthly income to income per year

@@

# Export data to use with Stata (gewicht hinzugefügt)
habe_bd_2010_unmarried <- rbind(data.frame(cbind("income" = habe10.unmarried$inc_habe,"group"=0,"weight"=habe10.unmarried$gew)),data.frame("income" = bd.2010.ind,"group"=1,"weight"=1))
habe_bd_2010_unmarried$group <- factor(habe_bd_2010_unmarried$group,labels=c("habe","bd"))
write.dta(habe_bd_2010_unmarried, file="../../data/stata_data/habe_bd_2010_unmarried.dta")
